---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# konigsbergr

[![Travis build status](https://travis-ci.org/dSHARP-CMU/konigsbergr.svg?branch=master)](https://travis-ci.org/dSHARP-CMU/konigsbergr)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/dSHARP-CMU/konigsbergr?branch=master&svg=true)](https://ci.appveyor.com/project/dSHARP-CMU/konigsbergr)
[![Coverage status](https://codecov.io/gh/dSHARP-CMU/konigsbergr/branch/master/graph/badge.svg)](https://codecov.io/github/dSHARP-CMU/konigsbergr?branch=master)

The goal of konigsbergr is to recreate the "Bridges of Königsberg" problem over any city by converting data from OpenStreetMap into a graph and traversing it.

## Installation

You can install the development version:

```{r, eval = FALSE}
devtools::install_github("dSHARP-CMU/konigsbergr")
```

## Usage

Konigsbergr works with OSM data, transforming it into a graph object and then using the [pathfinder] package to traverse edges within it.

```{r}
library(konigsbergr)

boston_osm <- get_osm_bbox(xmin = -71.1383,
                           xmax = -71.1132,
                           ymin = 42.3592,
                           ymax = 42.3754)
boston_osm

boston_graph <- konigsberg_graph(boston_osm)

boston_pathway <- cross_all_bridges(boston_graph)

view_konigsberg_path(boston_graph, boston_pathway)
```
