---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# konigsbergr

[![Travis build status](https://travis-ci.org/dSHARP-CMU/konigsbergr.svg?branch=master)](https://travis-ci.org/dSHARP-CMU/konigsbergr)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/dSHARP-CMU/konigsbergr?branch=master&svg=true)](https://ci.appveyor.com/project/dSHARP-CMU/konigsbergr)
[![Coverage status](https://codecov.io/gh/dSHARP-CMU/konigsbergr/branch/master/graph/badge.svg)](https://codecov.io/github/dSHARP-CMU/konigsbergr?branch=master)

The goal of konigsbergr is to recreate the "Bridges of Königsberg" problem over any city by converting data from OpenStreetMap into a graph and traversing it.

## Installation

You can install the development version:

```{r, eval = FALSE}
devtools::install_github("dSHARP-CMU/konigsbergr")
```

## Usage

Get OSM data

Project it into a graph and identify bridge attributes
  - subset for roads
  - subset for pedestrians
  - subset for custom
  
Run "pathfinder"

Visualize with SF/leaflet
