---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# konigsbergr

[![Travis build status](https://travis-ci.org/cmu-lib/konigsbergr.svg?branch=master)](https://travis-ci.org/cmu-lib/konigsbergr)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/cmu-lib/konigsbergr?branch=master&svg=true)](https://ci.appveyor.com/project/cmu-lib/konigsbergr)
[![Coverage status](https://codecov.io/gh/cmu-lib/konigsbergr/branch/master/graph/badge.svg)](https://codecov.io/github/cmu-lib/konigsbergr?branch=master)

The goal of konigsbergr is to recreate the ["Bridges of Königsberg"](https://en.wikipedia.org/wiki/Seven_Bridges_of_K%C3%B6nigsberg) problem over any city by converting data from OpenStreetMap into a graph and traversing it.

## Installation

You can install the development version:

```{r install, eval = FALSE}
# install.packages("remotes")
remotes::install_github("cmu-lib/konigsbergr")
```

## Usage

Konigsbergr works with OSM data, transforming it into a graph object and then using the [pathfinder] package to traverse edges within it. The result is a pathway that will try to cross all the bridges in a given city.

For the complete manual, see [the package vignette](https://cmu-lib.github.io/konigsbergr/articles/konigsbergr.html).

## Context

This package is one of several originally developed by [Matthew Lincoln](https:://github.com/mdlincoln) for use by Carnegie Mellon University's ["Bridges of Pittsburgh"](http://bridgesofpittsburgh.net/) project:

- [konigsberger] (end-user package)
  - [pathfinder]
  - [bigosm]

[konigsberger]: https://cmu-lib.github.io/konigsbergr/index.html

[pathfinder]: https://github.com/cmu-lib/pathfinder/

[bigosm]: https://github.com/cmu-lib/bigosm
